---
title: "12-starter-code"
format: docx
editor: visual
---

This lecture is about data pre-processing. Think about pre-processing as data cleaning for models.

We have already done some pre-processing: data splitting.

```{r message=FALSE}
# Load packages.
library(tidyverse)
library(tidymodels)

# Import soup data.
soup_data <- read_csv("soup_data.csv")

# Split data.
soup_split <- initial_time_split(soup_data, prop = 0.90)
```

Preprocessing data is made easier using the recipes package where common preprocessing tasks have been broken down into steps, beginning with a `recipe()` where we identify the model outcome and explanatory variables (a.k.a., predictors) using *formula* notation.

```{r}
(soup_recipe <- training(soup_split) |> 
  recipe(Sales ~ Any_Disp_Spend + Any_Price_Decr_Spend + Sub_Category))
```

One common pre-processing step is to check for right-skewed continuous variables.

```{r}
# Visualize Sales.
soup_data |> 
  ggplot(aes(x = Sales)) +
  geom_histogram()
```

Let's check the distributions of all continuous variables in our data.

```{r}
# Visualize all continuous variables.
soup_data |> 
  pivot_longer(
    c(Sales, Any_Disp_Spend, Any_Price_Decr_Spend),
    names_to = "var_names",
    values_to = "cont_values"
  ) |> 
  ggplot(aes(x = cont_values)) +
  geom_histogram() + 
  facet_wrap(~ var_names)
```

We address skewed variables because our linear regression model assumes that our error term $\epsilon$ is normally distributed. Skewed variables can cause that assumption to be violated.

We notice some rows were removed for the previous plot. Let's verify that this was due to missing values.

```{r}
soup_data |> 
  filter(is.na(Sales) | is.na(Any_Disp_Spend) | is.na(Any_Price_Decr_Spend)) |> 
  select(Sales, Any_Disp_Spend, Any_Price_Decr_Spend)
```

Let's reconstruct the plot without the missing values.

```{r echo=FALSE}
# Visualize all continuous variables.
soup_data |> 
  filter(!is.na(Sales), !is.na(Any_Disp_Spend), !is.na(Any_Price_Decr_Spend)) |>
  pivot_longer(
    c(Sales, Any_Disp_Spend, Any_Price_Decr_Spend),
    names_to = "var_names",
    values_to = "cont_values"
  ) |> 
  ggplot(aes(x = cont_values)) +
  geom_histogram() + 
  facet_wrap(~ var_names)
```

All four of these variables we've plotted have been right-skewed. We can fix that using a log-transformation. Let's plot what the log-transformed variables look like.

```{r eval=FALSE}
# Use the log() transform.
soup_data |> 
  pivot_longer(
    c(Sales, Any_Disp_Spend, Any_Price_Decr_Spend),
    names_to = "var_names",
    values_to = "cont_values"
  ) |> 
  mutate(log_cont_values = log(cont_values + 1)) |> 
  ggplot(aes(x = log_cont_values)) +
  geom_histogram() + 
  facet_wrap(~ var_names, scales = "free")
```







