---
title: "12-starter-code"
format: docx
editor: visual
---

This lecture is about data pre-processing. Think about pre-processing as data cleaning for models.

We have already done some pre-processing: data splitting.

```{r message=FALSE}
# Load packages.
library(tidyverse)
library(tidymodels)

# Import soup data.
soup_data <- read_csv("soup_data.csv")

# Split data.
soup_split <- initial_time_split(soup_data, prop = 0.90)
```

Preprocessing data is made easier using the recipes package where common preprocessing tasks have been broken down into steps, beginning with a `recipe()` where we identify the model outcome and explanatory variables (a.k.a., predictors) using *formula* notation.

```{r}
(soup_recipe <- training(soup_split) |> 
  recipe(Sales ~ Any_Disp_Spend + Any_Price_Decr_Spend + Sub_Category))
```

# Right-Skewed Continuous Variables

One common pre-processing step is to check for right-skewed continuous variables.

```{r}
# Visualize Sales.
soup_data |> 
  ggplot(aes(x = Sales)) +
  geom_histogram()
```

Let's check the distributions of all continuous variables in our data.

```{r}
# Visualize all continuous variables.
soup_data |> 
  pivot_longer(
    c(Sales, Any_Disp_Spend, Any_Price_Decr_Spend),
    names_to = "var_names",
    values_to = "cont_values"
  ) |> 
  ggplot(aes(x = cont_values)) +
  geom_histogram() + 
  facet_wrap(~ var_names)
```

We address skewed variables because our linear regression model assumes that our error term $\epsilon$ is normally distributed. Skewed variables can cause that assumption to be violated.

We notice some rows were removed for the previous plot. Let's verify that this was due to missing values.

```{r}
soup_data |> 
  filter(is.na(Sales) | is.na(Any_Disp_Spend) | is.na(Any_Price_Decr_Spend)) |> 
  select(Sales, Any_Disp_Spend, Any_Price_Decr_Spend)
```

Let's reconstruct the plot without the missing values.

```{r}
# Visualize all continuous variables.
soup_data |> 
  filter(!is.na(Sales), !is.na(Any_Disp_Spend), !is.na(Any_Price_Decr_Spend)) |>
  pivot_longer(
    c(Sales, Any_Disp_Spend, Any_Price_Decr_Spend),
    names_to = "var_names",
    values_to = "cont_values"
  ) |> 
  ggplot(aes(x = cont_values)) +
  geom_histogram() + 
  facet_wrap(~ var_names)
```

All four of these variables we've plotted have been right-skewed. We can fix that using a log-transformation. Let's plot what the log-transformed variables look like.

```{r eval=FALSE}
# Use the log() transform.
soup_data |>
  filter(!is.na(Sales), !is.na(Any_Disp_Spend), !is.na(Any_Price_Decr_Spend)) |>
  pivot_longer(
    c(Sales, Any_Disp_Spend, Any_Price_Decr_Spend),
    names_to = "var_names",
    values_to = "cont_values"
  ) |> 
  mutate(log_cont_values = log(cont_values + 1)) |> 
  ggplot(aes(x = log_cont_values)) +
  geom_histogram() + 
  facet_wrap(~ var_names, scales = "free")
```

Add the log transformation step to the recipe. Apply to all numeric predictions.

```{r}
# offset = 1 adds 1 to the variables before applying the log - this prevents us from
# applying log to 0.
(soup_recipe <- training(soup_split) |> 
  recipe(Sales ~ Any_Disp_Spend + Any_Price_Decr_Spend + Sub_Category) |> 
  step_log(all_numeric(), offset = 1))
```

# Discrete Variables

In additional to right-skewed continuous variables, we also need to pre-process discrete variables. How many binary variables will we have when we dummy code this discrete variable?

```{r}
soup_data |> 
  count(Sub_Category)
```

We add this step to our recipe using `step_dummy()`. We could reference all discrete variables in the model with `all_nominal()`.

```{r}
soup_recipe <- training(soup_split) |> 
  recipe(Sales ~ Any_Disp_Spend + Any_Price_Decr_Spend + Sub_Category) |> 
  step_log(all_numeric(), offset = 1) |> 
  step_dummy(Sub_Category)

soup_recipe
```

## Prepare a Recipe

We can build the recipe all at once. Once we're ready, we can `prep()` the recipe using the training data. The resulting object is a complete recipe that we can apply to whatever data we'd like.

```{r}
soup_recipe <- training(soup_split) |> 
  recipe(Sales ~ Any_Disp_Spend + Any_Price_Decr_Spend + Sub_Category) |>
  step_log(all_numeric(), offset = 1) |> 
  step_dummy(Sub_Category) |> 
  prep()
```

## Apply a Recipe

Following the recipe analogy, we apply a prepared recipe to data using `bake()`.

```{r}
# Apply the recipe to the training data.
baked_soup_training <- soup_recipe |>
  bake(training(soup_split))
```

Check out the baked training data.

```{r}
baked_soup_training
```

## Fit with Preprocessed Training Data

Let's compare models with and without the preprocessed data.

```{r}
# Fit a model without preprocessed data.
fit_raw <- linear_reg() |> 
  set_engine("lm") |> 
  fit(
    Sales ~ Any_Disp_Spend + Any_Price_Decr_Spend + Sub_Category, 
    data = training(soup_split)
  )

# Fit a model with preprocessed data.
fit_baked <- linear_reg() |> 
  set_engine("lm") |> 
  fit(
    Sales ~ ., 
    data = baked_soup_training
  )
```

## Evaluate Parameter Estimates

```{r}
fit_baked |>
  tidy()
```


If we want to use it, there is a horizontal version of the error bars plot.

Error Bar plot for 'Raw' Data

```{r}
# Compare parameter estimates.
tidy(fit_raw, conf.int = TRUE) |> 
  ggplot(aes(y = term)) + 
  geom_point(aes(x = estimate)) + 
  geom_errorbar(aes(xmin = conf.low, xmax = conf.high), orientation = 'y') +
  geom_vline(xintercept = 0, color = "red")
```

Error Bar plot for Pre-processed Data

```{r}
# Compare parameter estimates.
tidy(fit_baked, conf.int = TRUE) |> 
  ggplot(aes(y = term)) + 
  geom_point(aes(x = estimate)) + 
  geom_errorbar(aes(xmin = conf.low, xmax = conf.high), orientation = 'y') +
  geom_vline(xintercept = 0, color = "red")
```

## Your Turn!

We need to compute the RMSE of our two models using the testing data. Make sure to apply all necessary pre-processing steps to the testing data before applying the model that was trained on the pre-processed training data.

```{r}
# Apply the recipe to the testing data.
# THIS is why recipes are so helpful - they allow you to save 
# your pre-processing steps and apply them across different data frames
baked_soup_testing <- soup_recipe |>
  bake(testing(soup_split))

bind_rows(
  # Compute RMSE without preprocessed testing data.
  predict(fit_raw, new_data = testing(soup_split)) |>
    bind_cols(testing(soup_split)) |>
    rmse(truth = Sales, estimate = .pred),
  # Compute RMSE with preprocessed testing data.
  predict(fit_baked, new_data = baked_soup_testing) |>
    bind_cols(baked_soup_testing) |>
    rmse(truth = Sales, estimate = .pred)
)
```

Model comparison on raw scale.

```{r}
bind_rows(
  # Compute RMSE without preprocessed testing data.
  predict(fit_raw, new_data = testing(soup_split)) |>
    bind_cols(testing(soup_split)) |>
    rmse(truth = Sales, estimate = .pred),
  # Compute RMSE after transforming predictions from preprocessed testing data
  predict(fit_baked, new_data = baked_soup_testing) |>
    bind_cols(testing(soup_split)) |>
    mutate(.pred = exp(.pred)) |>
    rmse(truth = Sales, estimate = .pred)
)
```

Model comparison on log scale.

```{r}
bind_rows(
  # Compute RMSE after transforming predictions from raw testing data.
  predict(fit_raw, new_data = testing(soup_split)) |>
    bind_cols(baked_soup_testing) |>
    mutate(.pred = log(.pred)) |>
    rmse(truth = Sales, estimate = .pred),
  # Compute RMSE for predictions from preprocessed testing data
  predict(fit_baked, new_data = baked_soup_testing) |>
    bind_cols(baked_soup_testing) |>
    rmse(truth = Sales, estimate = .pred)
)
```

## Apply a Recipe to Counterfactuals

Having all of the preprocessing steps saved as a recipe means we can easily apply it to `new_data` when using `predict()` to evaluate counterfactuals. Construct the counterfactual data in the same form as the raw data so that it will work with our recipe.

Revisit what the raw data looks like.

```{r}
soup_data |>
  select(Any_Disp_Spend, Any_Price_Decr_Spend, Sub_Category, Sales)
```

# Construct Counterfactuals

Allocate \$10,000 spend between display and price decreases for each sub-category.

```{r}
# Counterfactual scenarios.
scenarios <- tibble(
  # compute display spend numbers, repeat them 5 times, once for each category
  Any_Disp_Spend = seq(from = 0, to = 10000, by = 2000) |> rep(5),
  # compute price decrease spend numbers, repeat them 5 times, once for each category
  Any_Price_Decr_Spend = seq(from = 10000, to = 0, by = -2000) |> rep(5),
  # character vector of subcategories, repeated six times six we have six counterfactual scenarios
  # in each sub-category
  Sub_Category = unique(soup_data$Sub_Category) |> rep(6) |> sort(),
  Sales = 1
)
```

What's different about this `new_data`? How can we interpret each of the rows?

```{r}
scenarios
```

Apply the recipe and remove the outcome variable before using the new data for `predict()`.

```{r}
# Apply the recipe to the training data.
baked_scenarios <- soup_recipe |>
  bake(scenarios) |> 
  select(-Sales)

baked_scenarios
```

Generate point predictions and predictive intervals.

```{r}
# Predict and bind on prediction intervals.
bind_cols(
  predict(fit_baked, new_data = baked_scenarios),
  predict(fit_baked, new_data = baked_scenarios, type = "pred_int"),
  baked_scenarios
) |> 
  arrange(desc(.pred))
```

Which scenario is the best?

# Live Coding

Our old client, **iFood**, has requested an updated model for total sales. Now that we have knowledge of various pre-processing skills, let's build and assess a new model for them.

```{r}

```
